SAT Solving for Vesicle Traffic Systems in Cells

### 2017-07-20 paper/experiments.tex
asd

% C_es :Self edges are allowed
% C_ed : Every edge is distinct 
  \end{tabular}
\caption{{\bf Activity regulation of molecules vs. graph connectivity.}}
\label{tab:grph}
\end{table}

@@

In the table~\ref{tab:grph}, we also present the minimum connectedness needed for
the different variants after applying our tool for sizes from 2 to 10.
%
We haven't found any graph for the variant A with constraints Ann and Aen.
%
Replacing constraint on the node of Ann with Anb (version B) does not affect the outcome.
%
If we allow every present molecule to stay active (Ann) but constraint the edge
by a boolean function (Aeb) the resultant VTS has to be at least 3-connected.
%
If we constrain the activity of both the edge and the nodes with the boolean function (Anb and Aeb), 
the VTS has to be 2-connected.
%
Similarly, the results for the other cases are also presented in the table.

@@

>>>>

% C_es :Self edges are allowed
% C_ed : Every edge is distinct 
  \end{tabular}
\caption{{\bf Activity regulation of molecules vs. graph connectivity.}}
\label{tab:grph}
\vspace{-5ex}
\end{table}

@@

To illustrate usability of our tool 
in last column of the table~\ref{tab:grph}, we also present the minimum connectedness
needed for the different variants after applying our tool for sizes from 2 to 10.
%
We found no graph for the variant A with constraints Ann and Aen.
%
Replacing constraint on the node of Ann with Anb (variant B) does not affect the outcome.
%
If we allow every present molecule to stay active (Ann) but constraint the edge
by a boolean function (Aeb) the resultant VTS has to be at least 3-connected.
%
% If we constrain the activity of both the edge and the nodes with the boolean function (Anb and Aeb), 
% the VTS has to be 2-connected.
%
Similarly, the results for the other cases are presented in the table.

@@

% \vspace{-3ex}
